Constructing a universe for the setoid model

### 2020-07-08 paper.tex
Compress concls to stay within 15 pgs

Additionally, we want to figure out whether our inductive encoding of the setoid
universe can support universe induction. A related question is whether the
alternative definitions using induction-recursion and induction-induction can
support it.

Another question regards the relationship between SeTT \cite{mpc19} and XTT
\cite{xtt}. Both systems are syntactic representations of the setoid model with
similar design choices, like definitional proof-irrelevance. We would like to
know whether their respective notions of models are equivalent.
In particular, we would like to obtain an XTT model from a SeTT model, and vice versa. Since XTT
universes support universe induction, for one direction we would need to
extend our own universe with the same principle (see discussion in
Section~\ref{sec:setoid-model} and the previous paragraph). A further question is
whether this mapping of models is functorial.

The groupoid model of type theory \cite{groupoid} can be seen as a
generalization of the setoid model, since groupoids are essentially
proof-relevant setoids.
%
One question is therefore whether it is possible to design a type theory
internalizing the groupoid model, in the same way that SeTT represents a syntax
for the setoid model. A further question is whether such ``groupoid type
theory'' can be justified, similarly to SeTT, via a syntactic translation,
perhaps with SeTT itself as the target theory.

>>>>

Another question regards the relationship between SeTT \cite{mpc19} and XTT
\cite{xtt}. Both systems are syntactic representations of the setoid model with
similar design choices, like definitional proof-irrelevance. We would like to
know whether their respective notions of models are equivalent, that is, if we
can obtain an XTT model from a SeTT model, and vice versa. Since XTT universes
support universe induction, for one direction we would need to extend our own
universe with the same principle (see discussion in
Section~\ref{sec:setoid-model} and the previous paragraph). Thus a related
question is whether our encodings of the setoid universe can support universe
induction. A further question is whether this mapping of models is functorial.

Groupoids can be regarded as generalized setoids. In the future we would like to
design a type theory internalizing the groupoid model of type theory
\cite{groupoid}, in the same way that SeTT represents a syntax for the setoid
model. A further question is whether such ``groupoid type theory'' can be
justified, similarly to SeTT, via a syntactic translation, perhaps with SeTT
itself as the target theory.
